Appendix

### 2025-12-15 manuscript_rmarkdown/manuscript_appendix.Rmd
Update scale for assessing transformation using simulated data.

# Appendix C: Central normality test and empirical central normality test critical values

@@

```
\begin{table}
\begin{center}
\caption{
Comparison of average rank between Box-Cox transformation methods based on either residual error (without outliers) or residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 100000 sequences each. The clean dataset consists of sequences derived through inverse Box-Cox transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 100, and scaled by 0.001.
If necessary, each sequence was shifted so that every element had a strictly positive value. 
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A rank of 1 is the best and a rank of 9 the worst. For each dataset, the best ranking transformation is marked in bold.
}
\label{tab:comparison_methods_simulations_box_cox}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & &         7.63  &         6.95  &         7.29  &         6.59  &         7.47  &         6.78 \\
conventional                          & &         3.11  &         5.98  &         5.41  &         6.18  &         6.51  &         6.10 \\
conventional (z-score norm.)          & &         4.15  &         6.27  &         4.83  &         6.32  &         4.34  &         5.84 \\
conventional (robust scaling)         & &         4.20  &         6.29  &         4.84  &         6.31  &         4.35  &         5.84 \\
Raymaekers-Rousseeuw                  & &         4.50  &         3.56  &         5.39  &         3.69  &         6.30  &         5.80 \\ 
Raymaekers-Rousseeuw (z-score norm.)  & &         6.23  &         3.80  &         4.93  &         3.85  &         4.48  &         3.50 \\ 
Raymaekers-Rousseeuw (robust scaling) & &         6.12  &         3.80  &         4.99  &         3.87  &         4.53  &         3.51 \\
invariant                             & & \textbf{2.96} &         5.59  & \textbf{3.62} &         6.01  & \textbf{3.51} &         5.58 \\
robust invariant                      & &         6.10  & \textbf{2.76} &         3.68  & \textbf{2.19} & \textbf{3.51} & \textbf{2.00} \\

@@

\begin{table}
\begin{center}
\caption{
Comparison of average normalised residual error between Yeo-Johnson transformation methods based on either the residual error (without outliers) or the residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 100000 sequences each. Residual errors were normalised by sequence length to reduce the effect of sequence length on the residual error.
The clean dataset consists of sequences derived through inverse Yeo-Johnson transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions, centred at 0.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 100, and scaled by 0.001.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A lower normalised residual error is better. Discrepancies with the rank-based method may occur, as even with normalisation residual errors 
are not fully comparable between experiments, whereas the ranks achieved within each experiment are.
}
\label{tab:comparison_methods_simulations_yeo_johnson_avg_residual}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & & 0.202 & 0.112 & 0.128 & 0.080 & 0.129 & 0.080 \\
conventional                          & & 0.058 & 0.094 & 0.085 & 0.078 & 0.129 & 0.080 \\
conventional (z-score norm.)          & & 0.061 & 0.094 & 0.091 & 0.073 & 0.091 & 0.073 \\
conventional (robust scaling)         & & 0.058 & 0.094 & 0.090 & 0.073 & 0.090 & 0.073 \\
Raymaekers-Rousseeuw                  & & 0.071 & 0.055 & 0.092 & 0.279 & 0.129 & 0.080 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.087 & 0.057 & 0.097 & 0.060 & 0.097 & 0.060 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.071 & 0.056 & 0.095 & 0.059 & 0.095 & 0.059 \\
invariant                             & & 0.057 & 0.099 & 0.083 & 0.075 & 0.083 & 0.075 \\
robust invariant                      & & 0.069 & 0.066 & 0.084 & 0.058 & 0.084 & 0.058 \\

@@

\begin{table}
\begin{center}
\caption{
Comparison of average difference in residual error between Yeo-Johnson
transformation methods and the best transformation method within each
experiment, normalised by the corresponding sequence length. This is based on
either the residual error (without outliers) or the residual error of the
central portion (with outliers; $\kappa = 0.80$) over 3 datasets with 100000
sequences each. Residual errors were normalised by sequence length to reduce the
effect of sequence length on the residual error. The clean dataset consists of
sequences derived through inverse Yeo-Johnson transformation of data sampled
from a standard normal distribution. The dirty dataset contains sequences
sampled from asymmetric generalised normal distributions, centred at 0. The
shifted dataset also contains sequences sampled from asymmetric generalised
normal distributions, but centred at 100, and scaled by 0.001. Several
transformation methods include normalisation before transformation, indicated by
z-score normalisation (norm.) or robust scaling. A lower difference is better,
with a minimum value of 0.0. Discrepancies with the rank-based method may occur,
as normalised differences in residual error are not fully comparable between
experiments, whereas the ranks achieved within each experiment are.
}
\label{tab:comparison_methods_simulations_yeo_johnson_avg_residual_diff}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & & 0.150 & 0.068 & 0.050 & 0.033 & 0.049 & 0.033 \\
conventional                          & & 0.005 & 0.049 & 0.006 & 0.032 & 0.049 & 0.033 \\
conventional (z-score norm.)          & & 0.008 & 0.049 & 0.013 & 0.026 & 0.011 & 0.025 \\
conventional (robust scaling)         & & 0.005 & 0.050 & 0.012 & 0.026 & 0.010 & 0.026 \\
Raymaekers-Rousseeuw                  & & 0.018 & 0.011 & 0.014 & 0.233 & 0.049 & 0.033 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.034 & 0.012 & 0.018 & 0.014 & 0.017 & 0.013 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.018 & 0.011 & 0.017 & 0.012 & 0.015 & 0.011 \\
invariant                             & & 0.004 & 0.054 & 0.005 & 0.029 & 0.003 & 0.028 \\
robust invariant                      & & 0.016 & 0.021 & 0.006 & 0.011 & 0.004 & 0.010 \\

@@

\begin{table}
\begin{center}
\caption{
Comparison of average rank between Yeo-Johnson transformation methods based on either residual error (without outliers) or residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 16001 sequences each. Each sequence contained 30 samples or fewer. 
The clean dataset consists of sequences derived through inverse Yeo-Johnson transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions, centred at 0.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 100, and scaled by 0.001.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A rank of 1 is the best and a rank of 9 the worst. For each dataset, the best ranking transformation is marked in bold.
}
\label{tab:comparison_methods_simulations_yeo_johnson_10_30}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & &         7.75  &         6.81  &         7.27  &         6.40  &         7.45  &         6.60 \\
conventional                          & &         4.19  &         5.47  &         4.48  &         5.78  &         6.55  &         5.94 \\
conventional (z-score norm.)          & &         4.36  &         5.12  &         5.01  &         4.99  &         4.35  &         4.70 \\
conventional (robust scaling)         & & \textbf{4.05} &         5.63  &         4.38  &         5.49  &         3.76  &         5.20 \\
Raymaekers-Rousseeuw                  & &         5.36  &         4.19  &         5.14  &         4.62  &         6.32  &         5.83 \\
Raymaekers-Rousseeuw (z-score norm.)  & &         5.56  &         4.08  &         5.67  &         4.05  &         5.03  &         3.81 \\
Raymaekers-Rousseeuw (robust scaling) & &         5.33  &         4.14  &         5.15  &         4.15  &         4.55  &         3.94 \\
invariant                             & &         4.11  &         5.92  &         4.12  &         5.67  &         3.62  &         5.37 \\
robust invariant                      & &         4.28  & \textbf{3.65} & \textbf{3.79} & \textbf{3.85} & \textbf{3.37} & \textbf{3.61} \\

@@

\begin{table}
\begin{center}
\caption{
Comparison of average normalised residual error between Yeo-Johnson transformation methods based on either the residual error (without outliers) or the residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 16001 sequences each. Residual errors were normalised by sequence length to reduce the effect of sequence length on the residual error.
Each sequence contained 30 samples or fewer. The clean dataset consists of sequences derived through inverse Yeo-Johnson transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions, centred at 0.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 100, and scaled by 0.001.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A lower normalised residual error is better. Discrepancies with the rank-based method may occur, as even with normalisation residual errors 
are not fully comparable between experiments, whereas the ranks achieved within each experiment are.
}
\label{tab:comparison_methods_simulations_yeo_johnson_10_30_avg_residual}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & & 0.246 & 0.173 & 0.186 & 0.156 & 0.187 & 0.157 \\
conventional                          & & 0.139 & 0.142 & 0.142 & 0.132 & 0.187 & 0.157 \\
conventional (z-score norm.)          & & 0.139 & 0.142 & 0.142 & 0.130 & 0.142 & 0.130 \\
conventional (robust scaling)         & & 0.139 & 0.142 & 0.141 & 0.130 & 0.141 & 0.130 \\
Raymaekers-Rousseeuw                  & & 0.211 & 0.151 & 0.183 & 1.515 & 0.187 & 0.157 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.295 & 0.161 & 0.175 & 0.156 & 0.175 & 0.156 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.209 & 0.155 & 0.172 & 0.144 & 0.172 & 0.144 \\
invariant                             & & 0.141 & 0.144 & 0.140 & 0.132 & 0.140 & 0.132 \\
robust invariant                      & & 0.141 & 0.125 & 0.140 & 0.119 & 0.140 & 0.119 \\

@@

\begin{table}
\begin{center}
\caption{
Comparison of average rank between Yeo-Johnson transformation methods based on either residual error (without outliers) or residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 33037 sequences each. Each sequence contained between 1000 and 10000 samples.
The clean dataset consists of sequences derived through inverse Yeo-Johnson transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions, centred at 0.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 100, and scaled by 0.001.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A rank of 1 is the best and a rank of 9 the worst. For each dataset, the best ranking transformation is marked in bold.
}
\label{tab:comparison_methods_simulations_yeo_johnson_1000_10000}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & &         8.85  &         8.14  &         7.35  &         6.29  &         7.41  &         6.87 \\
conventional                          & &         3.50  &         5.65  &         3.52  &         7.78  &         6.42  &         6.05 \\
conventional (z-score norm.)          & &         5.24  &         5.94  &         7.34  &         4.98  &         6.26  &         4.79 \\
conventional (robust scaling)         & &         3.53  &         6.98  &         5.97  &         5.79  &         4.87  &         5.65 \\
Raymaekers-Rousseeuw                  & &         4.15  &         2.81  &         3.37  &         3.72  &         6.19  &         5.79 \\
Raymaekers-Rousseeuw (z-score norm.)  & &         5.34  & \textbf{1.86} &         6.57  &         3.39  &         5.49  &         3.30 \\
Raymaekers-Rousseeuw (robust scaling) & &         4.20  &         2.33  &         5.21  &         3.36  &         4.12  &         3.23 \\
invariant                             & & \textbf{2.36} &         7.59  & \textbf{2.66} &         6.82  & \textbf{1.98} &         6.81 \\
robust invariant                      & &         7.83  &         3.70  &         3.01  & \textbf{2.88} &         2.26  & \textbf{2.51} \\

@@

\begin{table}
\begin{center}
\caption{
Comparison of average normalised residual error between Yeo-Johnson transformation methods based on either the residual error (without outliers) or the residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 16001 sequences each. Residual errors were normalised by sequence length to reduce the effect of sequence length on the residual error.
Each sequence contained between 1000 and 10000 samples. The clean dataset consists of sequences derived through inverse Yeo-Johnson transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions, centred at 0.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 100, and scaled by 0.001.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A lower normalised residual error is better. Discrepancies with the rank-based method may occur, as even with normalisation residual errors 
are not fully comparable between experiments, whereas the ranks achieved within each experiment are.
}
\label{tab:comparison_methods_simulations_yeo_johnson_1000_10000_avg_residual}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & & 0.186 & 0.091 & 0.106 & 0.053 & 0.106 & 0.053 \\
conventional                          & & 0.014 & 0.076 & 0.060 & 0.057 & 0.106 & 0.053 \\
conventional (z-score norm.)          & & 0.021 & 0.076 & 0.070 & 0.050 & 0.070 & 0.050 \\
conventional (robust scaling)         & & 0.014 & 0.076 & 0.069 & 0.050 & 0.069 & 0.050 \\
Raymaekers-Rousseeuw                  & & 0.015 & 0.021 & 0.060 & 0.030 & 0.106 & 0.053 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.021 & 0.020 & 0.070 & 0.030 & 0.070 & 0.030 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.015 & 0.020 & 0.068 & 0.030 & 0.068 & 0.030 \\
invariant                             & & 0.013 & 0.084 & 0.059 & 0.055 & 0.059 & 0.055 \\
robust invariant                      & & 0.034 & 0.042 & 0.061 & 0.032 & 0.061 & 0.032 \\

>>>>

# Appendix C: Empirical central normality test critical values

@@

```
\begin{table}
\begin{center}
\caption{
Comparison of average rank between Box-Cox transformation methods based on either residual error (without outliers) or residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 100000 sequences each. The clean dataset consists of sequences derived through inverse Box-Cox transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 1000.
If necessary, each sequence was shifted so that every element had a strictly positive value. 
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A rank of 1 is the best and a rank of 9 the worst. For each dataset, the best ranking transformation is marked in bold.
}
\label{tab:comparison_methods_simulations_box_cox}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & &         7.63  &         6.95  &         7.29  &         6.59  &         7.46  &         6.77 \\
conventional                          & &         3.11  &         5.98  &         5.41  &         6.18  &         6.51  &         6.26 \\
conventional (z-score norm.)          & &         4.15  &         6.27  &         4.83  &         6.32  &         4.39  &         5.96 \\
conventional (robust scaling)         & &         4.20  &         6.29  &         4.84  &         6.31  &         4.40  &         5.96 \\
Raymaekers-Rousseeuw                  & &         4.50  &         3.56  &         5.39  &         3.69  &         6.29  &         5.35 \\ 
Raymaekers-Rousseeuw (z-score norm.)  & &         6.23  &         3.80  &         4.93  &         3.85  &         4.53  &         3.51 \\ 
Raymaekers-Rousseeuw (robust scaling) & &         6.12  &         3.80  &         4.99  &         3.87  &         4.58  &         3.52 \\
invariant                             & & \textbf{2.96} &         5.59  & \textbf{3.62} &         6.01  & \textbf{3.53} &         5.67 \\
robust invariant                      & &         6.10  & \textbf{2.76} &         3.68  & \textbf{2.19} &         3.55  & \textbf{2.00} \\

@@

\begin{table}
\begin{center}
\caption{
Comparison of average normalised residual error between Yeo-Johnson transformation methods based on either the residual error (without outliers) or the residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 100000 sequences each. Residual errors were normalised by sequence length to reduce the effect of sequence length on the residual error.
The clean dataset consists of sequences derived through inverse Yeo-Johnson transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions, centred at 0.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 1000.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A lower normalised residual error is better. Discrepancies with the rank-based method may occur, as even with normalisation residual errors 
are not fully comparable between experiments, whereas the ranks achieved within each experiment are.
}
\label{tab:comparison_methods_simulations_yeo_johnson_avg_residual}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & & 0.202 & 0.112 & 0.128 & 0.080 & 0.129 & 0.080 \\
conventional                          & & 0.058 & 0.094 & 0.085 & 0.078 & 0.126 & 0.080 \\
conventional (z-score norm.)          & & 0.061 & 0.094 & 0.091 & 0.073 & 0.091 & 0.073 \\
conventional (robust scaling)         & & 0.058 & 0.094 & 0.090 & 0.073 & 0.090 & 0.073 \\
Raymaekers-Rousseeuw                  & & 0.071 & 0.055 & 0.092 & 0.279 & 0.126 & 0.079 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.087 & 0.057 & 0.097 & 0.060 & 0.097 & 0.060 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.071 & 0.056 & 0.095 & 0.059 & 0.095 & 0.059 \\
invariant                             & & 0.057 & 0.099 & 0.083 & 0.075 & 0.083 & 0.075 \\
robust invariant                      & & 0.069 & 0.066 & 0.084 & 0.058 & 0.084 & 0.058 \\

@@

\begin{table}
\begin{center}
\caption{
Comparison of average difference in residual error between Yeo-Johnson
transformation methods and the best transformation method within each
experiment, normalised by the corresponding sequence length. This is based on
either the residual error (without outliers) or the residual error of the
central portion (with outliers; $\kappa = 0.80$) over 3 datasets with 100000
sequences each. Residual errors were normalised by sequence length to reduce the
effect of sequence length on the residual error. The clean dataset consists of
sequences derived through inverse Yeo-Johnson transformation of data sampled
from a standard normal distribution. The dirty dataset contains sequences
sampled from asymmetric generalised normal distributions, centred at 0. The
shifted dataset also contains sequences sampled from asymmetric generalised
normal distributions, but centred at 1000. Several
transformation methods include normalisation before transformation, indicated by
z-score normalisation (norm.) or robust scaling. A lower difference is better,
with a minimum value of 0.0. Discrepancies with the rank-based method may occur,
as normalised differences in residual error are not fully comparable between
experiments, whereas the ranks achieved within each experiment are.
}
\label{tab:comparison_methods_simulations_yeo_johnson_avg_residual_diff}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & & 0.150 & 0.068 & 0.050 & 0.033 & 0.049 & 0.033 \\
conventional                          & & 0.005 & 0.049 & 0.006 & 0.032 & 0.046 & 0.032 \\
conventional (z-score norm.)          & & 0.008 & 0.049 & 0.013 & 0.026 & 0.011 & 0.025 \\
conventional (robust scaling)         & & 0.005 & 0.050 & 0.012 & 0.026 & 0.010 & 0.026 \\
Raymaekers-Rousseeuw                  & & 0.018 & 0.011 & 0.014 & 0.233 & 0.046 & 0.031 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.034 & 0.012 & 0.018 & 0.014 & 0.017 & 0.013 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.018 & 0.011 & 0.017 & 0.012 & 0.015 & 0.011 \\
invariant                             & & 0.004 & 0.054 & 0.005 & 0.029 & 0.003 & 0.028 \\
robust invariant                      & & 0.016 & 0.021 & 0.006 & 0.011 & 0.004 & 0.010 \\

@@

\begin{table}
\begin{center}
\caption{
Comparison of average rank between Yeo-Johnson transformation methods based on either residual error (without outliers) or residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 16001 sequences each. Each sequence contained 30 samples or fewer. 
The clean dataset consists of sequences derived through inverse Yeo-Johnson transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions, centred at 0.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 1000.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A rank of 1 is the best and a rank of 9 the worst. For each dataset, the best ranking transformation is marked in bold.
}
\label{tab:comparison_methods_simulations_yeo_johnson_10_30}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & &         7.75  &         6.81  &         7.27  &         6.40  &         7.44  &         6.59 \\
conventional                          & &         4.19  &         5.47  &         4.48  &         5.78  &         6.35  &         6.00 \\
conventional (z-score norm.)          & &         4.36  &         5.12  &         5.01  &         4.99  &         4.36  &         4.71 \\
conventional (robust scaling)         & & \textbf{4.05} &         5.63  &         4.38  &         5.49  &         3.77  &         5.21 \\
Raymaekers-Rousseeuw                  & &         5.36  &         4.19  &         5.14  &         4.62  &         6.47  &         5.72 \\
Raymaekers-Rousseeuw (z-score norm.)  & &         5.56  &         4.08  &         5.67  &         4.05  &         5.04  &         3.82 \\
Raymaekers-Rousseeuw (robust scaling) & &         5.33  &         4.14  &         5.15  &         4.15  &         4.56  &         3.95 \\
invariant                             & &         4.11  &         5.92  &         4.12  &         5.67  &         3.64  &         5.38 \\
robust invariant                      & &         4.28  & \textbf{3.65} & \textbf{3.79} & \textbf{3.85} & \textbf{3.37} & \textbf{3.62} \\

@@

\begin{table}
\begin{center}
\caption{
Comparison of average normalised residual error between Yeo-Johnson transformation methods based on either the residual error (without outliers) or the residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 16001 sequences each. Residual errors were normalised by sequence length to reduce the effect of sequence length on the residual error.
Each sequence contained 30 samples or fewer. The clean dataset consists of sequences derived through inverse Yeo-Johnson transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions, centred at 0.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 1000.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A lower normalised residual error is better. Discrepancies with the rank-based method may occur, as even with normalisation residual errors 
are not fully comparable between experiments, whereas the ranks achieved within each experiment are.
}
\label{tab:comparison_methods_simulations_yeo_johnson_10_30_avg_residual}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & & 0.246 & 0.173 & 0.186 & 0.156 & 0.187 & 0.157 \\
conventional                          & & 0.139 & 0.142 & 0.142 & 0.132 & 0.184 & 0.155 \\
conventional (z-score norm.)          & & 0.139 & 0.142 & 0.142 & 0.130 & 0.142 & 0.130 \\
conventional (robust scaling)         & & 0.139 & 0.142 & 0.141 & 0.130 & 0.141 & 0.130 \\
Raymaekers-Rousseeuw                  & & 0.211 & 0.151 & 0.183 & 1.515 & 0.185 & 0.155 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.295 & 0.161 & 0.175 & 0.156 & 0.175 & 0.156 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.209 & 0.155 & 0.172 & 0.144 & 0.172 & 0.144 \\
invariant                             & & 0.141 & 0.144 & 0.140 & 0.132 & 0.140 & 0.132 \\
robust invariant                      & & 0.141 & 0.125 & 0.140 & 0.119 & 0.140 & 0.119 \\

@@

\begin{table}
\begin{center}
\caption{
Comparison of average rank between Yeo-Johnson transformation methods based on either residual error (without outliers) or residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 33037 sequences each. Each sequence contained between 1000 and 10000 samples.
The clean dataset consists of sequences derived through inverse Yeo-Johnson transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions, centred at 0.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 1000.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A rank of 1 is the best and a rank of 9 the worst. For each dataset, the best ranking transformation is marked in bold.
}
\label{tab:comparison_methods_simulations_yeo_johnson_1000_10000}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & &         8.85  &         8.14  &         7.35  &         6.29  &         7.40  &         6.86 \\
conventional                          & &         3.50  &         5.65  &         3.52  &         7.78  &         6.24  &         6.45 \\
conventional (z-score norm.)          & &         5.24  &         5.94  &         7.34  &         4.98  &         6.29  &         4.92 \\
conventional (robust scaling)         & &         3.53  &         6.98  &         5.97  &         5.79  &         4.90  &         5.79 \\
Raymaekers-Rousseeuw                  & &         4.15  &         2.81  &         3.37  &         3.72  &         6.22  &         5.04 \\
Raymaekers-Rousseeuw (z-score norm.)  & &         5.34  & \textbf{1.86} &         6.57  &         3.39  &         5.52  &         3.35 \\
Raymaekers-Rousseeuw (robust scaling) & &         4.20  &         2.33  &         5.21  &         3.36  &         4.16  &         3.27 \\
invariant                             & & \textbf{2.36} &         7.59  & \textbf{2.66} &         6.82  & \textbf{1.99} &         6.82 \\
robust invariant                      & &         7.83  &         3.70  &         3.01  & \textbf{2.88} &         2.27  & \textbf{2.52} \\

@@

\begin{table}
\begin{center}
\caption{
Comparison of average normalised residual error between Yeo-Johnson transformation methods based on either the residual error (without outliers) or the residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 16001 sequences each. Residual errors were normalised by sequence length to reduce the effect of sequence length on the residual error.
Each sequence contained between 1000 and 10000 samples. The clean dataset consists of sequences derived through inverse Yeo-Johnson transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions, centred at 0.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 1000.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A lower normalised residual error is better. Discrepancies with the rank-based method may occur, as even with normalisation residual errors 
are not fully comparable between experiments, whereas the ranks achieved within each experiment are.
}
\label{tab:comparison_methods_simulations_yeo_johnson_1000_10000_avg_residual}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & & 0.186 & 0.091 & 0.106 & 0.053 & 0.106 & 0.053 \\
conventional                          & & 0.014 & 0.076 & 0.060 & 0.057 & 0.103 & 0.053 \\
conventional (z-score norm.)          & & 0.021 & 0.076 & 0.070 & 0.050 & 0.070 & 0.050 \\
conventional (robust scaling)         & & 0.014 & 0.076 & 0.069 & 0.050 & 0.069 & 0.050 \\
Raymaekers-Rousseeuw                  & & 0.015 & 0.021 & 0.060 & 0.030 & 0.103 & 0.051 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.021 & 0.020 & 0.070 & 0.030 & 0.070 & 0.030 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.015 & 0.020 & 0.068 & 0.030 & 0.068 & 0.030 \\
invariant                             & & 0.013 & 0.084 & 0.059 & 0.055 & 0.059 & 0.055 \\
robust invariant                      & & 0.034 & 0.042 & 0.061 & 0.032 & 0.061 & 0.032 \\
